Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
remove duplicate template text

While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they are difficult to author. Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, under failures and as the network evolves.

@@

Templates that work for one topology may not work for seemingly-inconsequential variations.  
%Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
Worse, when operators discover their old templates no longer work, changing a template will
cause a change to all devices that use that template---an unacceptable disruption in many cases.  When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
Such patches reintroduce the complexity and errors that templates were meant to prevent.

>>>>

%While templates help avoid a class of configuration errors (e.g., inconsistent routing adjacencies), they provide no guarantees
Templates that work for one topology may not work for seemingly-inconsequential variations.  
%Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
Worse, when operators discover their old templates no longer work, changing a template will
cause a change to all devices that use that template---an unacceptable disruption in many cases.  When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
Such patches reintroduce the complexity and errors that templates were meant to prevent.

%they are difficult to author. Operators must manually decompose complex, network-wide routing policy into role templates such that the collective behavior of the configurations generated from them will correctly implement the policy, both when failures occur and as the network evolves.

@@

%Templates that work for one topology may not work for seemingly-inconsequential variations.  
%Unfotunately, currently, there is no way to predict which variations will behave correctly for a given set of templates.
%Worse, when operators discover their old templates no longer work, changing a template will
%cause a change to all devices that use that template---an unacceptable disruption in many cases.  When that happens, operators may abandon templates entirely and revert to hand-crafting configurations, using local patches to accommodate the change.
%Such patches reintroduce the complexity and errors that templates were meant to prevent.
